Manuscript title here

### 2024-09-16 project-plan.Rmd
rättade till referens platsen

Trauma is a significant global public health concern, responsible for causing death and disability in over four million people each year. Among those affected, younger populations are more impacted, making trauma management a worldwide health care concern[@noauthor_injuries_nodate]. The initial management of trauma patients in the hospital setting is time-sensitive and prone to errors, which can adversely affect patient outcomes[@mackersie_pitfalls_2010]. Trauma patients presenting with shock have a notably higher mortality compared to those who are not in shock, underscoring the need for improved care strategies for these patients[@vang_shock_2022].
Shock is generally defined as circulatory failure resulting in insufficient perfusion and oxygenation of tissues and organs[@leech_shock_2023]. There are four primary causes of shock: hypovolemic, obstructive, cardiogenic and distributive. These etiologies can occur alone or in combination. In the context of trauma, hypovolemic shock, usually caused by massive hemorrhage, is the most common type of shock[@teixeira_preventable_2007].

>>>>

Trauma is a significant global public health concern, responsible for causing death and disability in over four million people each year. Among those affected, younger populations are more impacted, making trauma management a worldwide health care concern[@noauthor_injuries_nodate]. The initial management of trauma patients in the hospital setting is time-sensitive and prone to errors, which can adversely affect patient outcomes[@mackersie_pitfalls_2010]. Trauma patients presenting with shock have a notably higher mortality compared to those who are not in shock[@vang_shock_2022], underscoring the need for improved care strategies for these patients.
Shock is generally defined as circulatory failure resulting in insufficient perfusion and oxygenation of tissues and organs[@leech_shock_2023]. There are four primary causes of shock: hypovolemic, obstructive, cardiogenic and distributive. These etiologies can occur alone or in combination. In the context of trauma, hypovolemic shock, usually caused by massive hemorrhage, is the most common type of shock[@teixeira_preventable_2007].
